Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-03 article.tex
fixing the table size

\noindent{\bf Forward models and distributions}:
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
    single-scattering simulated images are used as input to the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[htbp]
  \centering
  \begin{tabular}{cccccgg}
    \toprule
    Scene      & Forward        & Aerosol density & Isotropic       & Absorbing & $\epsilon$ & Mass \\
               & model          & order           & Phase function? & aerosol?  &            & diff. \\
     \midrule
    Haze Front & Single scatter & $10^{6}$         &                 &           & 0.18       & 1.1\%  \\
               & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 14\%  \\
    \cmidrule(r){1-5}
    Haze Blobs & Single scatter & $10^{6}$         &                 &           & 0.14       & 0\%  \\
               & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 6.7\%  \\
               & Monte Carlo    & $10^{6}$         & $\surd$         &           & 0.49       & 2\%  \\
               & Monte Carlo    & $10^{6}$         &                 & $\surd$   & 0.83       & 9.6\%  \\
               & Monte Carlo    & $10^{7}$         &                 &           & 0.98       & 23\%  \\
    \bottomrule
  \end{tabular}
  \caption{Relative error measure in various simulations}
  \label{tbl:mass}
\end{table}
the algorithm of \cref{sec:inverse-problem}. \\

>>>>

\noindent{\bf Forward models and distributions}:
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In (a) and (b)
    single-scattering simulated images are used as input to the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[htbp]
  \centering
  \begin{tabular}{cccccgg}
    \toprule
    Scene      & Forward        & Aerosol          & Isotropic       & Absorbing & $\epsilon$ & Mass \\
               & model          & density order    & Phase function? & aerosol?  &            & diff. \\
     \midrule
    Haze       & Single scatter & $10^{6}$         &                 &           & 0.18       & 1.1\%  \\
    Front      & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 14\%  \\
    \cmidrule(r){1-5}
    Haze       & Single scatter & $10^{6}$         &                 &           & 0.14       & 0\%  \\
    Blobs      & Monte Carlo    & $10^{6}$         &                 &           & 0.65       & 6.7\%  \\
               & Monte Carlo    & $10^{6}$         & $\surd$         &           & 0.49       & 2\%  \\
               & Monte Carlo    & $10^{6}$         &                 & $\surd$   & 0.83       & 9.6\%  \\
               & Monte Carlo    & $10^{7}$         &                 &           & 0.98       & 23\%  \\
    \bottomrule
  \end{tabular}
  \caption{Relative error measure in various simulations}
  \label{tbl:mass}
\end{table}
the algorithm of \cref{sec:inverse-problem}. \\
